Proportional multi-state multiple-cohort life table model

### 2018-04-13 MSLT/MSLTdoc.Rmd
Added function to run comparison plots GBD data

```{r, echo=FALSE}
###TO DO: loops for sex, cause and measure and interpolation of rates, care with interpolating rates, need to convert to log for interpolation using cubic spline. 
#FOR NOW THE CODE FOR GRAPH IS repetitive
####################MORTALITY RATES ALL CAUSE PER ONE

>>>>

```{r, echo=FALSE}
###TO DO: loops for sex, cause and measure and interpolation of rates, care with interpolating rates, need to convert to log for interpolation using cubic spline. 
#FOR NOW THE CODE FOR GRAPH IS repetitive

#in_data1: GBDEngland
#in_data2: GBDGL
#in_sex: male, female
#in_cause: all causes, ischemic heart disease, ischemic stroke, diabetes mellitus, colon and rectum cancers, breast cancer, tracheal, bronchus, and lung cancer
#in_measure: deaths, incidence, prevalence, ylds (years lived with disability)

plot_GBD_compare_death_all_cause_males <- function(in_data1 = GBDEngland, in_data2 = GBDGL, in_sex = "male", in_cause = "all causes", in_measure = "deaths")
